Figures and tables for paper

### 2021-12-04 analysis/04_figs-tables.Rmd
Attempt #1 at contrasts with main effects. Hypotheses 4c, 5d and 5e need to be fixed.
I forgot to commit the actual coding changes, somehow. This should do it.

```{r}
# Read in interaction draws for contrasts
intib <- read_rds(
    here::here("analysis", "output", "posterior_draws", "interactions.rds")
  )

# Storing intercept draws in a different tibble for easier use; emergency response, no financial transparency, no accountability, many private donors and friendly relationship with government are all reference levels for their respective groups, and thus are not found in the tibble.
dtib <- tibble(
  amnesty = draws %>% filter(i == 1) %>% select(Gamma) %>% pull(),
  greenpeace = draws %>% filter(i == 2) %>% select(Gamma) %>% pull(),
  oxfam = draws %>% filter(i == 3) %>% select(Gamma) %>% pull(),
  red_cross = draws %>% filter(i == 4)%>% select(Gamma) %>% pull(),
  environment = draws %>% filter(i == 5) %>% select(Gamma) %>% pull(),
  human_rights = draws %>% filter(i == 6) %>% select(Gamma) %>% pull(),
  refugee_relief = draws %>% filter(i == 7) %>% select(Gamma) %>% pull(),
  fin_transparency = draws %>% filter(i == 8)%>% select(Gamma) %>% pull(),
  accountability = draws %>% filter(i == 9) %>% select(Gamma) %>% pull(),
  few_wealthy_private_donors = draws %>% filter(i == 10) %>% select(Gamma) %>% pull(),
  government_grants = draws %>% filter(i == 11) %>% select(Gamma) %>% pull(),
  criticized = draws %>% filter(i == 12)%>% select(Gamma) %>% pull(),
  crackdown = draws %>% filter(i == 13) %>% select(Gamma) %>% pull()
)
```

@@

```{r crackdown-contrasts-b}
# Overwrite draws with the appropriate interaction data
draws <- here::here("analysis", "output", "posterior_draws", "interactions_2b.rds")

@@

contrasts_int <- tibble(
  amnesty_criticized = intib %>% filter(i == 14) %>% select(Gamma) %>% pull(),
  greenpeace_criticized = intib %>% filter(i == 15) %>% select(Gamma) %>% pull(),
  oxfam_criticized = intib %>% filter(i == 16) %>% select(Gamma) %>% pull(),
  red_cross_criticized = intib %>% filter(i == 17)%>% select(Gamma) %>% pull(),
  amnesty_crackdown = intib %>% filter(i == 18) %>% select(Gamma) %>% pull(),
  greenpeace_crackdown = intib %>% filter(i == 19) %>% select(Gamma) %>% pull(),
  oxfam_crackdown = intib %>% filter(i == 20) %>% select(Gamma) %>% pull(),
  red_cross_crackdown = intib %>% filter(i == 21)%>% select(Gamma) %>% pull()
) %>% 
  mutate(
    oxfam_amnesty_criticized = ((dtib$oxfam + oxfam_criticized) - (dtib$amnesty + amnesty_criticized) + dtib$criticized),
    oxfam_greenpeace_criticized = ((dtib$oxfam + oxfam_criticized) - (dtib$greenpeace + greenpeace_criticized) + dtib$criticized),
    red_cross_amnesty_criticized = ((dtib$red_cross + red_cross_criticized) - (dtib$amnesty + amnesty_criticized) + dtib$criticized),
    red_cross_greenpeace_criticized = ((dtib$red_cross + red_cross_criticized) - (dtib$greenpeace + greenpeace_criticized) + dtib$criticized),
    oxfam_amnesty_crackdown = ((dtib$oxfam + oxfam_crackdown) - (dtib$amnesty + amnesty_crackdown) + dtib$crackdown),
    oxfam_greenpeace_crackdown = ((dtib$oxfam + oxfam_crackdown) - (dtib$greenpeace + greenpeace_crackdown) + dtib$crackdown),
    red_cross_amnesty_crackdown = ((dtib$red_cross + red_cross_crackdown) - (dtib$amnesty + amnesty_crackdown) + dtib$crackdown),
    red_cross_greenpeace_crackdown = ((dtib$red_cross + red_cross_crackdown) - (dtib$greenpeace + greenpeace_crackdown) + dtib$crackdown)
  )

@@

```{r crackdown-contrasts-b-alt}
# Overwrite draws with the appropriate interaction data
draws <- here::here("analysis", "output", "posterior_draws", "interactions_2b.rds")

contrasts_int <- tibble(
  amnesty_criticized = intib %>% filter(i == 14) %>% select(Gamma) %>% pull(),
  greenpeace_criticized = intib %>% filter(i == 15) %>% select(Gamma) %>% pull(),
  oxfam_criticized = intib %>% filter(i == 16) %>% select(Gamma) %>% pull(),
  red_cross_criticized = intib %>% filter(i == 17)%>% select(Gamma) %>% pull(),
  amnesty_crackdown = intib %>% filter(i == 18) %>% select(Gamma) %>% pull(),
  greenpeace_crackdown = intib %>% filter(i == 19) %>% select(Gamma) %>% pull(),
  oxfam_crackdown = intib %>% filter(i == 20) %>% select(Gamma) %>% pull(),
  red_cross_crackdown = intib %>% filter(i == 21)%>% select(Gamma) %>% pull()
) %>% 
  mutate(
    oxfam_amnesty_criticized = (dtib$oxfam + oxfam_criticized) - (dtib$amnesty + amnesty_criticized),
    oxfam_greenpeace_criticized = (dtib$oxfam + oxfam_criticized) - (dtib$greenpeace + greenpeace_criticized),
    red_cross_amnesty_criticized = (dtib$red_cross + red_cross_criticized) - (dtib$amnesty + amnesty_criticized),
    red_cross_greenpeace_criticized = (dtib$red_cross + red_cross_criticized) - (dtib$greenpeace + greenpeace_criticized),
    oxfam_amnesty_crackdown = (dtib$oxfam + oxfam_crackdown) - (dtib$amnesty + amnesty_crackdown),
    oxfam_greenpeace_crackdown = (dtib$oxfam + oxfam_crackdown) - (dtib$greenpeace + greenpeace_crackdown),
    red_cross_amnesty_crackdown = (dtib$red_cross + red_cross_crackdown) - (dtib$amnesty + amnesty_crackdown),
    red_cross_greenpeace_crackdown = (dtib$red_cross + red_cross_crackdown) - (dtib$greenpeace + greenpeace_crackdown)
  )

# Save plot
ggsave(
  "contrasts_hypothesis02b_alt.png",
  path = here::here("analysis", "output", "figures"),
  width = 12,
  height = 6,
  units = "in"
 )
```

@@

```{r issue-contrasts-a}
# Pull the posterior draws for issue area
# Reference Level = Emergency Response

contrasts <- tibble(
  environment = draws %>% filter(level == "Environment") %>% select(Gamma) %>% pull(),
  human_rights = draws %>% filter(level == "Human rights") %>% select(Gamma) %>% pull(),
  refugee_relief = draws %>% filter(level == "Refugee relief") %>% select(Gamma) %>% pull()
  )

@@

```{r issue-contrasts-b}
# Overwrite draws with the appropriate interaction data
draws <- here::here("analysis", "output", "posterior_draws", "interactions_3b.rds")

@@

contrasts_int <- tibble(
  criticized_environment = intib %>% filter(i == 22) %>% select(Gamma) %>% pull(),
  criticized_humanrights = intib %>% filter(i == 23) %>% select(Gamma) %>% pull(),
  criticized_refugee = intib %>% filter(i == 24) %>% select(Gamma) %>% pull(),
  crackdown_environment = intib %>% filter(i == 25) %>% select(Gamma) %>% pull(),
  crackdown_humanrights = intib %>% filter(i == 26) %>% select(Gamma) %>% pull(),
  crackdown_refugee = intib %>% filter(i == 27) %>% select(Gamma) %>% pull(),
) %>% 
  mutate(
  criticized_refugee_environment = criticized_refugee - criticized_environment,
  criticized_refugee_humanrights = criticized_refugee - criticized_humanrights,
  crackdown_refugee_environment = crackdown_refugee - crackdown_environment,
  crackdown_refugee_humanrights = crackdown_refugee - crackdown_humanrights
)

@@

```{r funding-contrasts-a}
# Pull the posterior draws for funding sources
# Reference Level = Funded primarily by many small private donations

contrasts <- tibble(
  few_wealthy_private_donors = draws %>% filter(level == "Handful of wealthy private donors") %>% select(Gamma) %>% pull(),
  government_grants = draws %>% filter(level == "Government grants") %>% select(Gamma) %>% pull()
  )

@@

```{r funding-contrasts-b}
# Overwrite draws with the appropriate interaction data
draws <- here::here("analysis", "output", "posterior_draws", "interactions_4b.rds")

@@

contrasts_int <- tibble(
  criticized_wealthydonors = intib %>% filter(i == 28) %>% select(Gamma) %>% pull(),
  criticized_grants = intib %>% filter(i == 29) %>% select(Gamma) %>% pull(),
  crackdown_wealthydonors = intib %>% filter(i == 30) %>% select(Gamma) %>% pull(),
  crackdown_grants = intib %>% filter(i == 31) %>% select(Gamma) %>% pull(),
)

@@

```{r funding-contrasts-c}
# Overwrite draws with the appropriate interaction data
draws <- here::here("analysis", "output", "posterior_draws", "interactions_4c.rds")

@@

contrasts_int <- tibble(
  emergency_crackdown_wealthydonors = intib %>% filter(i == 32) %>% select(Gamma) %>% pull(),
  emergency_crackdown_grants = intib %>% filter(i == 33) %>% select(Gamma) %>% pull(),
  environment_crackdown_wealthydonors = intib %>% filter(i == 34) %>% select(Gamma) %>% pull(),
  environment_crackdown_grants = intib %>% filter(i == 35) %>% select(Gamma) %>% pull(),
  humanrights_crackdown_wealthydonors = intib %>% filter(i == 36) %>% select(Gamma) %>% pull(),
  humanrights_crackdown_grants = intib %>% filter(i == 37) %>% select(Gamma) %>% pull(),
  refugee_crackdown_wealthydonors = intib %>% filter(i == 38) %>% select(Gamma) %>% pull(),
  refugee_crackdown_grants = intib %>% filter(i == 39) %>% select(Gamma) %>% pull(),
) %>% 
  mutate(
  emergency_humanrights_wealthydonors = emergency_crackdown_wealthydonors - humanrights_crackdown_wealthydonors ,
  emergency_environment_wealthydonors = emergency_crackdown_wealthydonors - environment_crackdown_wealthydonors,
  emergency_grants_wealthydonors = emergency_crackdown_wealthydonors - emergency_crackdown_grants,
  refugee_humanrights_wealthydonors = refugee_crackdown_wealthydonors - humanrights_crackdown_wealthydonors,
  refugee_environment_wealthydonors = refugee_crackdown_wealthydonors - environment_crackdown_wealthydonors,
  refugee_grants_wealthydonors = refugee_crackdown_grants - refugee_crackdown_wealthydonors
  )

# Plot the contrasts
contrasts_int %>%
  pivot_longer(emergency_humanrights_wealthydonors:refugee_grants_wealthydonors, names_to = "level", values_to = "Gamma") %>% 
  ggplot(aes(x = Gamma, y = level)) +
  stat_halfeye(.width = .95) +
  geom_vline(xintercept = 0, color = "grey") +
  labs(y = "Difference in Attribute Levels", x = "Difference in Gammas")

@@

```{r practices-contrasts-a}
# Pull the posterior draws for organizational practices

contrasts <- tibble(
  financial_transparency = draws %>% filter(level == "Financial transparency") %>% select(Gamma) %>% pull(),
  accountability = draws %>% filter(level == "Accountability") %>% select(Gamma) %>% pull()
  )

@@

```{r practices-contrasts-b}
# Overwrite draws with the appropriate interaction data
draws <- here::here("analysis", "output", "posterior_draws", "interactions_5b.rds")

@@

contrasts_int <- tibble(
  financial_transparency_criticized = intib %>% filter(i == 40) %>% select(Gamma) %>% pull(),
  financial_transparency_crackdown = intib %>% filter(i == 41) %>% select(Gamma) %>% pull(),
  )

@@

```{r practices-contrasts-c}
# Overwrite draws with the appropriate interaction data
draws <- here::here("analysis", "output", "posterior_draws", "interactions_5c.rds")

@@

contrasts_int <- tibble(
  fin_smalldonors_criticized = intib %>% filter(i == 42) %>% select(Gamma) %>% pull(),
  fin_wealthydonors_criticized = intib %>% filter(i == 43) %>% select(Gamma) %>% pull(),
  fin_grants_criticized = intib %>% filter(i == 44) %>% select(Gamma) %>% pull(),
  fin_smalldonors_crackdown = intib %>% filter(i == 45) %>% select(Gamma) %>% pull(),
  fin_wealthydonors_crackdown = intib %>% filter(i == 46) %>% select(Gamma) %>% pull(),
  fin_grants_crackdown = intib %>% filter(i == 47) %>% select(Gamma) %>% pull(),
  ) %>%
  mutate(
  fin_smalldonors_wealthydonors_criticized = fin_smalldonors_criticized - fin_wealthydonors_criticized,
  fin_smalldonors_grants_criticized = fin_smalldonors_criticized - fin_grants_criticized,
  fin_smalldonors_wealthydonors_crackdown = fin_smalldonors_crackdown - fin_wealthydonors_crackdown,
  fin_smalldonors_grants_crackdown = fin_smalldonors_crackdown - fin_grants_crackdown
  )

@@

```{r practices-contrasts-d}
# Overwrite draws with the appropriate interaction data
draws <- here::here("analysis", "output", "posterior_draws", "interactions_5d.rds")

@@

contrasts_int <- tibble(
  fin_emergency_criticized = intib %>% filter(i == 48) %>% select(Gamma) %>% pull(),
  fin_emergency_crackdown = intib %>% filter(i == 49) %>% select(Gamma) %>% pull(),
  fin_environment_criticized = intib %>% filter(i == 50) %>% select(Gamma) %>% pull(),
  fin_environment_crackdown = intib %>% filter(i == 51) %>% select(Gamma) %>% pull(),
  fin_humanrights_criticized = intib %>% filter(i == 52) %>% select(Gamma) %>% pull(),
  fin_humanrights_crackdown = intib %>% filter(i == 53) %>% select(Gamma) %>% pull(),
  fin_refugee_criticized = intib %>% filter(i == 54) %>% select(Gamma) %>% pull(),
  fin_refugee_crackdown = intib %>% filter(i == 55) %>% select(Gamma) %>% pull()
  ) %>%
  mutate(
  fin_emergency_environment_criticized = fin_emergency_criticized - fin_environment_criticized,
  fin_emergency_humanrights_criticized = fin_emergency_criticized - fin_humanrights_criticized,
  fin_emergency_environment_crackdown = fin_emergency_crackdown - fin_environment_crackdown,
  fin_emergency_humanright_crackdown = fin_emergency_crackdown - fin_humanrights_crackdown,
  fin_refugee_environment_criticized = fin_refugee_criticized - fin_environment_criticized,
  fin_refugee_humanright_criticized = fin_refugee_criticized - fin_humanrights_criticized,
  fin_refugee_environment_crackdown = fin_refugee_crackdown - fin_environment_crackdown,
  fin_refugee_humanright_crackdown = fin_refugee_crackdown - fin_humanrights_crackdown
)

@@

```{r practices-contrasts-e}
# Overwrite draws with the appropriate interaction data
draws <- here::here("analysis", "output", "posterior_draws", "interactions_5e.rds")

@@

```{r practices-contrasts-b}
# Pull the posterior draws for organizational practices
contrasts <- tibble(
  financial_transparency = draws %>% filter(level == "Financial transparency") %>% select(Gamma) %>% pull(),
  accountability = draws %>% filter(level == "Accountability") %>% select(Gamma) %>% pull()
)

>>>>

```{r}
#storing intercept draws for easier reference
draws_intercepts <- draws
```

@@

```{r crackdown-contrasts-b}
# Overwrite draws with the appropriate interaction data

draws <- read_rds(here::here("data", "raw_data", "posterior_draws", "interactions_2b.rds"))

@@

contrasts_int <- tibble(
  amnesty = draws %>% filter(i == 1) %>% select(Gamma) %>% pull(),
  greenpeace = draws %>% filter(i == 2) %>% select(Gamma) %>% pull(),
  oxfam = draws %>% filter(i == 3) %>% select(Gamma) %>% pull(),
  red_cross = draws %>% filter(i == 4)%>% select(Gamma) %>% pull(),
  environment = draws %>% filter(i == 5) %>% select(Gamma) %>% pull(),
  human_rights = draws %>% filter(i == 6) %>% select(Gamma) %>% pull(),
  refugee_relief = draws %>% filter(i == 7) %>% select(Gamma) %>% pull(),
  fin_transparency = draws %>% filter(i == 8)%>% select(Gamma) %>% pull(),
  accountability = draws %>% filter(i == 9) %>% select(Gamma) %>% pull(),
  few_wealthy_private_donors = draws %>% filter(i == 10) %>% select(Gamma) %>% pull(),
  government_grants = draws %>% filter(i == 11) %>% select(Gamma) %>% pull(),
  criticized = draws %>% filter(i == 12)%>% select(Gamma) %>% pull(),
  crackdown = draws %>% filter(i == 13) %>% select(Gamma) %>% pull(),
  amnesty_criticized = draws %>% filter(i == 14) %>% select(Gamma) %>% pull(),
  greenpeace_criticized = draws %>% filter(i == 15) %>% select(Gamma) %>% pull(),
  oxfam_criticized = draws %>% filter(i == 16) %>% select(Gamma) %>% pull(),
  red_cross_criticized = draws %>% filter(i == 17)%>% select(Gamma) %>% pull(),
  amnesty_crackdown = draws %>% filter(i == 18) %>% select(Gamma) %>% pull(),
  greenpeace_crackdown = draws %>% filter(i == 19) %>% select(Gamma) %>% pull(),
  oxfam_crackdown = draws %>% filter(i == 20) %>% select(Gamma) %>% pull(),
  red_cross_crackdown = draws %>% filter(i == 21)%>% select(Gamma) %>% pull()
) %>% 
  mutate(
    oxfam_amnesty_criticized = (oxfam + criticized + oxfam_criticized) - (amnesty + criticized + amnesty_criticized),

    oxfam_greenpeace_criticized = (oxfam + criticized + oxfam_criticized) - (greenpeace + criticized + greenpeace_criticized),

    red_cross_amnesty_criticized = (red_cross + criticized + red_cross_criticized) - (amnesty + criticized + amnesty_criticized),

    red_cross_greenpeace_criticized = (red_cross + criticized + red_cross_criticized) - (greenpeace + criticized + greenpeace_criticized),

    oxfam_amnesty_crackdown = (oxfam + crackdown + oxfam_crackdown) - (amnesty + crackdown +  amnesty_crackdown),

    oxfam_greenpeace_crackdown = (oxfam + crackdown + oxfam_crackdown) - (greenpeace + crackdown +  greenpeace_crackdown),

    red_cross_amnesty_crackdown = (red_cross + crackdown + red_cross_crackdown) - (amnesty + crackdown +  amnesty_crackdown),

    red_cross_greenpeace_crackdown = (red_cross + crackdown + red_cross_crackdown) - (greenpeace + crackdown + greenpeace_crackdown)
  )

@@

@@

```{r issue-contrasts-a}
# Pull the posterior draws for issue area
# Reference Level = Emergency Response
draws <- draws_intercepts
contrasts <- tibble(
  environment = draws %>% filter(level == "Environment") %>% select(Gamma) %>% pull(),
  human_rights = draws %>% filter(level == "Human rights") %>% select(Gamma) %>% pull(),
  refugee_relief = draws %>% filter(level == "Refugee relief") %>% select(Gamma) %>% pull()
  )

@@

```{r issue-contrasts-b}
# Overwrite draws with the appropriate interaction data
draws <- read_rds(here::here("data", "raw_data", "posterior_draws", "interactions_3b.rds"))

@@

contrasts_int <- tibble(
  environment = draws %>% filter(i == 5) %>% select(Gamma) %>% pull(),
  human_rights = draws %>% filter(i == 6) %>% select(Gamma) %>% pull(),
  refugee_relief = draws %>% filter(i == 7) %>% select(Gamma) %>% pull(),
  criticized = draws %>% filter(i == 12)%>% select(Gamma) %>% pull(),
  crackdown = draws %>% filter(i == 13) %>% select(Gamma) %>% pull(),
  criticized_environment = draws %>% filter(i == 14) %>% select(Gamma) %>% pull(),
  criticized_humanrights = draws %>% filter(i == 15) %>% select(Gamma) %>% pull(),
  criticized_refugee = draws %>% filter(i == 16) %>% select(Gamma) %>% pull(),
  crackdown_environment = draws %>% filter(i == 17) %>% select(Gamma) %>% pull(),
  crackdown_humanrights = draws %>% filter(i == 18) %>% select(Gamma) %>% pull(),
  crackdown_refugee = draws %>% filter(i == 19) %>% select(Gamma) %>% pull(),
) %>% 
  mutate(
  criticized_refugee_environment = (criticized + refugee_relief + criticized_refugee) - (criticized + environment + criticized_environment),

  criticized_refugee_humanrights = (criticized + refugee_relief + criticized_refugee) - (criticized + human_rights + criticized_humanrights),

  crackdown_refugee_environment = (crackdown + refugee_relief + crackdown_refugee - crackdown + environment + crackdown_environment),

  crackdown_refugee_humanrights = (crackdown + refugee_relief + crackdown_refugee - crackdown + human_rights + crackdown_humanrights)
)

@@

```{r funding-contrasts-a}
# Pull the posterior draws for funding sources
# Reference Level = Funded primarily by many small private donations
draws <- draws_intercepts
contrasts <- tibble(
  few_wealthy_private_donors = draws %>% filter(level == "Handful of wealthy private donors") %>% select(Gamma) %>% pull(),
  government_grants = draws %>% filter(level == "Government grants") %>% select(Gamma) %>% pull()
  )

@@

```{r funding-contrasts-b}
# Overwrite draws with the appropriate interaction data
draws <- read_rds(here::here("data", "raw_data", "posterior_draws", "interactions_4b.rds"))

@@

contrasts_int <- tibble(
  few_wealthy_private_donors = draws %>% filter(i == 10) %>% select(Gamma) %>% pull(),
  government_grants = draws %>% filter(i == 11) %>% select(Gamma) %>% pull(),
  criticized = draws %>% filter(i == 12)%>% select(Gamma) %>% pull(),
  crackdown = draws %>% filter(i == 13) %>% select(Gamma) %>% pull(),
  criticized_wealthydonors = draws %>% filter(i == 14) %>% select(Gamma) %>% pull(),
  criticized_grants = draws %>% filter(i == 15) %>% select(Gamma) %>% pull(),
  crackdown_wealthydonors = draws %>% filter(i == 16) %>% select(Gamma) %>% pull(),
  crackdown_grants = draws %>% filter(i == 17) %>% select(Gamma) %>% pull(),
) %>% mutate(
  criticized_wealthydonors = (criticized + few_wealthy_private_donors + criticized_wealthydonors) - criticized,

  criticized_grants = (criticized + government_grants + criticized_grants) - criticized,

  crackdown_wealthydonors = (crackdown + few_wealthy_private_donors + crackdown_wealthydonors) - crackdown,

  crackdown_grants = (crackdown + government_grants + crackdown_grants) - crackdown
)

@@

```{r funding-contrasts-c}
# Overwrite draws with the appropriate interaction data
draws <- read_rds(here::here("data", "raw_data", "posterior_draws", "interactions_4c.rds"))

@@

contrasts_int <- tibble(
  environment = draws %>% filter(i == 5) %>% select(Gamma) %>% pull(),
  human_rights = draws %>% filter(i == 6) %>% select(Gamma) %>% pull(),
  refugee_relief = draws %>% filter(i == 7) %>% select(Gamma) %>% pull(),
  few_wealthy_private_donors = draws %>% filter(i == 10) %>% select(Gamma) %>% pull(),
  government_grants = draws %>% filter(i == 11) %>% select(Gamma) %>% pull(),
  criticized = draws %>% filter(i == 12)%>% select(Gamma) %>% pull(),
  crackdown = draws %>% filter(i == 13) %>% select(Gamma) %>% pull(),
  emergency_crackdown_wealthydonors = draws %>% filter(i == 14) %>% select(Gamma) %>% pull(),
  emergency_crackdown_grants = draws %>% filter(i == 15) %>% select(Gamma) %>% pull(),
  environment_crackdown_wealthydonors = draws %>% filter(i == 16) %>% select(Gamma) %>% pull(),
  environment_crackdown_grants = draws %>% filter(i == 17) %>% select(Gamma) %>% pull(),
  humanrights_crackdown_wealthydonors = draws %>% filter(i == 18) %>% select(Gamma) %>% pull(),
  humanrights_crackdown_grants = draws %>% filter(i == 19) %>% select(Gamma) %>% pull(),
  refugee_crackdown_wealthydonors = draws %>% filter(i == 20) %>% select(Gamma) %>% pull(),
  refugee_crackdown_grants = draws %>% filter(i == 21) %>% select(Gamma) %>% pull(),
) %>% 
  mutate(
  emergency_humanrights_wealthydonors = (crackdown + emergency_crackdown_wealthydonors) - (crackdown + few_wealthy_private_donors + human_rights + humanrights_crackdown_wealthydonors),

  emergency_humanrights_grants = (crackdown + emergency_crackdown_grants) - (crackdown + government_grants + human_rights + humanrights_crackdown_grants),

  emergency_environment_wealthydonors = (crackdown + emergency_crackdown_wealthydonors) - (crackdown + few_wealthy_private_donors + environment + environment_crackdown_wealthydonors),

  emergency_environment_grants = (crackdown + emergency_crackdown_grants) - (crackdown + government_grants + environment + environment_crackdown_wealthydonors),

  refugee_humanrights_wealthydonors = (crackdown + refugee_relief + refugee_crackdown_wealthydonors) - (crackdown + few_wealthy_private_donors + human_rights + humanrights_crackdown_wealthydonors),

  refugee_humanrights_grants = (crackdown + refugee_relief + refugee_crackdown_grants) - (crackdown + government_grants +  human_rights + humanrights_crackdown_grants),

  refugee_environment_wealthydonors = (crackdown + refugee_relief + refugee_crackdown_wealthydonors) - (crackdown + few_wealthy_private_donors + environment + environment_crackdown_wealthydonors),

  refugee_environment_grants = (crackdown + refugee_relief + refugee_crackdown_grants) - (crackdown + government_grants + environment + environment_crackdown_grants),

# Plot the contrasts
contrasts_int %>%
  pivot_longer(emergency_humanrights_wealthydonors:refugee_environment_grants, names_to = "level", values_to = "Gamma") %>% 
  ggplot(aes(x = Gamma, y = level)) +
  stat_halfeye(.width = .95) +
  geom_vline(xintercept = 0, color = "grey") +
  labs(y = "Difference in Attribute Levels", x = "Difference in Gammas")

@@

```{r practices-contrasts-a}
# Pull the posterior draws for organizational practices
draws <- draws_intercepts
contrasts <- tibble(
  financial_transparency = draws %>% filter(level == "Financial transparency") %>% select(Gamma) %>% pull(),
  accountability = draws %>% filter(level == "Accountability") %>% select(Gamma) %>% pull()
)

@@

```{r practices-contrasts-b}
# Overwrite draws with the appropriate interaction data
draws <- read_rds(here::here("data", "raw_data", "posterior_draws", "interactions_5b.rds"))

@@

contrasts_int <- tibble(
  fin_transparency = draws %>% filter(i == 8)%>% select(Gamma) %>% pull(),
  criticized = draws %>% filter(i == 12)%>% select(Gamma) %>% pull(),
  crackdown = draws %>% filter(i == 13) %>% select(Gamma) %>% pull(),
  financial_transparency_criticized = draws %>% filter(i == 14) %>% select(Gamma) %>% pull(),
  financial_transparency_crackdown = draws %>% filter(i == 15) %>% select(Gamma) %>% pull(),
  ) %>% mutate(
    financial_transparency_criticized = fin_transparency + criticized + financial_transparency_criticized,
    financial_transparency_crackdown = fin_transparency + crackdown + financial_transparency_crackdown
  )

@@

```{r practices-contrasts-c}
# Overwrite draws with the appropriate interaction data
draws <- read_rds(here::here("data", "raw_data", "posterior_draws", "interactions_5c.rds"))

@@

contrasts_int <- tibble(
  fin_transparency = draws %>% filter(i == 8)%>% select(Gamma) %>% pull(),
  few_wealthy_private_donors = draws %>% filter(i == 10) %>% select(Gamma) %>% pull(),
  government_grants = draws %>% filter(i == 11) %>% select(Gamma) %>% pull(),
  criticized = draws %>% filter(i == 12)%>% select(Gamma) %>% pull(),
  crackdown = draws %>% filter(i == 13) %>% select(Gamma) %>% pull(),
  fin_smalldonors_criticized = draws %>% filter(i == 14) %>% select(Gamma) %>% pull(),
  fin_wealthydonors_criticized = draws %>% filter(i == 15) %>% select(Gamma) %>% pull(),
  fin_grants_criticized = draws %>% filter(i == 16) %>% select(Gamma) %>% pull(),
  fin_smalldonors_crackdown = draws %>% filter(i == 17) %>% select(Gamma) %>% pull(),
  fin_wealthydonors_crackdown = draws %>% filter(i == 18) %>% select(Gamma) %>% pull(),
  fin_grants_crackdown = draws %>% filter(i == 19) %>% select(Gamma) %>% pull(),
  ) %>%
  mutate(
  fin_smalldonors_wealthydonors_criticized = (fin_transparency + criticized + fin_smalldonors_criticized) - (fin_transparency + criticized + few_wealthy_private_donors + fin_wealthydonors_criticized),

  fin_smalldonors_grants_criticized = (fin_transparency + criticized + fin_smalldonors_criticized) -  (fin_transparency + criticized + government_grants + fin_grants_criticized),

  fin_smalldonors_wealthydonors_crackdown = (fin_transparency + crackdown + fin_smalldonors_crackdown) - (fin_transparency + crackdown + few_wealthy_private_donors + fin_wealthydonors_crackdown),

  fin_smalldonors_grants_crackdown = (fin_transparency + crackdown + fin_smalldonors_crackdown) - (fin_transparency + crackdown + government_grants + fin_grants_crackdown)
  )

@@

```{r practices-contrasts-d}
# Overwrite draws with the appropriate interaction data
draws <- read_rds(here::here("data", "raw_data", "posterior_draws", "interactions_5d.rds"))

@@

contrasts_int <- tibble(
  fin_transparency = draws %>% filter(i == 8)%>% select(Gamma) %>% pull(),
  criticized = draws %>% filter(i == 12)%>% select(Gamma) %>% pull(),
  crackdown = draws %>% filter(i == 13) %>% select(Gamma) %>% pull(),
  environment = draws %>% filter(i == 5) %>% select(Gamma) %>% pull(),
  human_rights = draws %>% filter(i == 6) %>% select(Gamma) %>% pull(),
  refugee_relief = draws %>% filter(i == 7) %>% select(Gamma) %>% pull(),
  fin_emergency_criticized = draws %>% filter(i == 14) %>% select(Gamma) %>% pull(),
  fin_emergency_crackdown = draws %>% filter(i == 15) %>% select(Gamma) %>% pull(),
  fin_environment_criticized = draws %>% filter(i == 16) %>% select(Gamma) %>% pull(),
  fin_environment_crackdown = draws %>% filter(i == 17) %>% select(Gamma) %>% pull(),
  fin_humanrights_criticized = draws %>% filter(i == 18) %>% select(Gamma) %>% pull(),
  fin_humanrights_crackdown = draws %>% filter(i == 19) %>% select(Gamma) %>% pull(),
  fin_refugee_criticized = draws %>% filter(i == 20) %>% select(Gamma) %>% pull(),
  fin_refugee_crackdown = draws %>% filter(i == 21) %>% select(Gamma) %>% pull()
  ) %>%
  mutate(
  fin_emergency_environment_criticized = (fin_transparency + criticized + fin_emergency_criticized) - (fin_transparency + criticized + environment + fin_environment_criticized),

  fin_emergency_humanrights_criticized = (fin_transparency + criticized + fin_emergency_criticized) - fin_transparency + criticized + human_rights + fin_humanrights_criticized,

  fin_emergency_environment_crackdown = (fin_transparency + crackdown + fin_emergency_crackdown) - (fin_transparency + crackdown + environment + fin_environment_crackdown),

  fin_emergency_humanright_crackdown = (fin_transparency + crackdown + fin_emergency_crackdown) - (fin_transparency + crackdown + human_rights + fin_humanrights_crackdown),

  fin_refugee_environment_criticized = (fin_transparency + criticized + fin_refugee_criticized) - (fin_transparency + criticized + environment + fin_environment_criticized),

  fin_refugee_humanright_criticized = (fin_transparency + criticized + fin_refugee_criticized) - (fin_transparency + criticized + human_rights + fin_humanrights_criticized),

  fin_refugee_environment_crackdown = (fin_transparency + crackdown + fin_refugee_crackdown) - (fin_transparency + crackdown + environment + fin_environment_crackdown),

  fin_refugee_humanright_crackdown = (fin_transparency + crackdown + fin_refugee_crackdown) - (fin_transparency + crackdown + human_rights + fin_humanrights_crackdown)
)

@@

```{r practices-contrasts-e}
# Overwrite draws with the appropriate interaction data
draws <- read_rds(here::here("data", "raw_data", "posterior_draws", "interactions_5e.rds"))

@@

```{r practices-contrasts-b}
# Pull the posterior draws for organizational practices
draws <- draws_intercepts
contrasts <- tibble(
  financial_transparency = draws %>% filter(level == "Financial transparency") %>% select(Gamma) %>% pull(),
  accountability = draws %>% filter(level == "Accountability") %>% select(Gamma) %>% pull()
)
